Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-07-09 02_paper/02_study/paper_methods.Rmd
update method section

>>>>

XXX FRANZI 
```{r reaction_codingsystem, include=TRUE, echo=FALSE, results='asis'}

audit_table <- structure(
  list(
    Description = c(
      "The teacher reacts exclusively non-verbally to a disturbance. The flow of the lesson is not interrupted.",
      "The teacher reacts nonverbally and simultaneously with a short verbal reaction. The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixing gaze). The verbal response includes name calling, brief verbal prompts / admonitions.",
      "The teacher responds briefly and verbally to a disruption without a preceding nonverbal response.",
      "The teacher responds nonverbally and simultaneously overlapping with a verbal long response to a disruption. The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixating gaze).",
      "There is no reaction from the teacher to a disruption because the teacher does not consider it relevant to address the disruption. This information can only be obtained through the Stimulated Recall Interview.",
      "There is no reaction to a disruption on the part of the teacher because the teacher has not registered the disruption. This information can only be obtained through the Stimulated Recall Interview.",
      "Dysfunctional Response: the teacher responds inappropriately to a disruption through a lengthy verbal discussion of class rules, yelling around, etc."
                  ),
    `1` = c("Never", "1–2", "Never"),
    `2` = c("Monthly or less", "3-4", "Less than monthly"),
    `3` = c("2-4 times per month", "5-6", "monthly"),
    `4` = c("2-3 times per week","7-9", "Weekly"),
    `5` = c("4+ times per week", "10+", "Daily or almost daily"),
    `6` = c("bla"),
    `7` = c("bla")
          ),
  class = "data.frame",
  row.names = c(NA)
)

apa_table(
  audit_table,
  caption = "AUDIT-C scoring table",
  align = c("m{8cm}", rep("m{2cm}", 5)),
  col_spanners = list("Code" = c(2,7)),
  note = "Item scores are summed. Women who score 3+ and men who score 4+ are at-risk",
  landscape = TRUE
  )

# df_react_table <-
#   structure(list(
#     Code = c("1", "2", "3", "4", "5", "6", "7"),
#     Description = c(
#       "The teacher reacts exclusively non-verbally to a disturbance. The flow of the lesson is not interrupted.",
#       "The teacher reacts nonverbally and simultaneously with a short verbal reaction. The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixing gaze). The verbal response includes name calling, brief verbal prompts / admonitions.",
#       "The teacher responds briefly and verbally to a disruption without a preceding nonverbal response.",
#       "The teacher responds nonverbally and simultaneously overlapping with a verbal long response to a disruption. The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixating gaze).",
#       "There is no reaction from the teacher to a disruption because the teacher does not consider it relevant to address the disruption. This information can only be obtained through the Stimulated Recall Interview.",
#       "There is no reaction to a disruption on the part of the teacher because the teacher has not registered the disruption. This information can only be obtained through the Stimulated Recall Interview.",
#       "Dysfunctional Response: the teacher responds inappropriately to a disruption through a lengthy verbal discussion of class rules, yelling around, etc."
#     ),
#     `Anchor examples` = c("-",
#                           "-",
#                           "drawing on a sheet of paper",
#                           "-",
#                           "-",
#                           "-",
#                           "-"),
#     class = "data.frame"
#   ))
# 
# papaja::apa_table(
#   x = df_react_table,
#   caption = "Self-developed coding scheme for the teacher's reaction",
#   align = c("m{8cm}", rep("m{2cm}", 5)),
#   col_spanners = list("NA"),
#   # note = "",
#   landscape = TRUE)
